---
title: 'DH Quarterly Reporting - Model 1 Incidents'
author_details: "Alana Little, NEPHU (alana.little@austin.org.au)"
version_details: "v2.1, 12/01/2026"
output: 
  html_document: 
    code_folding: none
    toc: true
    toc_depth: 3
    toc_float: true
knit: (function(input, ...) {
  rmarkdown::render(input, output_file = paste0("2026 Q2", " DH Quarterly Reporting", " Model 1 Incidents"), output_dir = "../Reports") })
---

```{css, echo = FALSE}
/* */ 
.main-container {
    max-width: 1000px;
}

h1.title {
  font-weight: bold;
  font-size: 20px;
  color: #191d43;
}

h1 {
  font-weight: bold;
  font-size: 20px;
  color: #5bc788;
}

h2 {
  font-weight: bold;
  font-size: 18px;
  color: #5bc788;
}

h3 {
  font-weight: bold;
  font-size: 16px;
  color: #5bc788;
}

body {
  font-size: 14px;
}

.infobox {
  padding-top: 10px;
  padding-left: 10px;
  padding-right: 10px;
  background: white;
  color: black;
  border: 2px solid #5BC788;
  border-radius: 10px;
}
```


```{r, echo = FALSE, message = FALSE}
#
knitr::opts_chunk$set(echo    = FALSE, 
                      warning = FALSE, 
                      message = FALSE)

options(knitr.kable.NA = '--')

source(paste0(here::here(), "/Code", "/00_setup.R"))
```


```{r}
#
source(paste0(here::here(), "/Code", "/00_data_extract.R"))
```

:::{style="height: 1em;"}
:::

:::{.infobox}
**Indicator SQ1.6** 

**Number of incidents (Model 1)**

For the purposes of reporting a Model 1 incident refers to a one or more of the below scenarios occurring within a single LPHU catchment that does not meet the definition of a Model 2 or Model 3 incident:  

* A single case of a serious illness with major public health implications

* Two or more linked cases of unexplained illness that may be caused by the same known or unknown agent (an outbreak)  

* Higher than expected cases caused by or suspected to be caused by a serious pathogen

* A high risk of exposure to a hazard by a population
:::

## Total number of Model 1 Incidents

Data were extracted from PHESS via PHAR on `r format(Sys.Date(), format = "%d/%m/%Y")` for all notifiable conditions (cases) and outbreaks completed by NEPHU between `r format(quarter_start, format = "%d/%m/%Y")` and `r format(quarter_end, format = "%d/%m/%Y")`. 

* Both initial notifications and reinvestigations signed out for follow-up were included.

* Cases, contact/exposed persons, and outbreaks were included.

* Confirmed, Probable, Suspected, and At Risk notifications were included.

* Rejected and Not Notifiable notifications were excluded.

* Conditions not managed by LPHUs (anaphylaxis, elevated blood lead, human biosecurity reports, and tuberculosis) were excluded.

Model 1 incidents were defined as:

* Outbreaks of any pathogen

* Measles cases

* Invasive meningococcal disease cases

* Mpox cases

* Locally acquired typhoid, paratyphoid, or Hepatitis A cases

* Locally acquired legionellosis cases (excluding *L. longbeachae*)

* Locally acquired JEV, MEV, dengue, malaria, or yellow fever cases

* Overseas acquired typhoid, paratyphoid, Hepatitis A, or shigellosis cases who work in a high-risk occupation or attend childcare

* Invasive GAS cases where PEP provision was required

* Cases of high consequence pathogens (anthrax, avian influenza, botulism, cholera, diphtheria, HUS, lyssavirus, MERS, plague, polio, rabies, SARS, smallpox, tularemia, or viral haemorrhagic fevers)

:::{style="height: 1em;"}
:::

```{r}
# Closed outbreaks
nephu_incident_outbreaks <- outbreaks_nephu %>%
  dplyr::filter(event_classification %in% c("Confirmed", "Probable")) %>% 
  #
  dplyr::group_by(organism_cause) %>% 
  dplyr::summarise(n = n()) %>% 
  dplyr::ungroup() %>% 
  #
  janitor::adorn_totals()

outbreaks_total <- nephu_incident_outbreaks %>% 
  dplyr::filter(organism_cause == "Total") %>% 
  pull(n)
```


```{r}
# Confirmed and probable cases completed during reporting period
completed_nephu <- cases_nephu %>%
  dplyr::filter(event_classification %in% c("Confirmed", "Probable")) %>% 
  #
  dplyr::filter(investigation_status %in% c("Completed", "Reviewed") | reinvestigation_status %in% c("Completed", "Reviewed")) %>% 
  #
  dplyr::mutate(completed_quarter = dplyr::case_when(
    investigation_completed_date >= quarter_start & investigation_completed_date <= quarter_end ~ "Yes",
    reinvestigation_status_date >= quarter_start & reinvestigation_status_date <= quarter_end   ~ "Yes",
    TRUE ~ "No")) %>% 
  #
  dplyr::filter(completed_quarter == "Yes") %>% 
  #
  # Q2 2026 only - exclude bulk closure of historical gono cases
  dplyr::filter(!c(condition == "Gonococcal infection" & event_date < lubridate::ymd("2025-10-24") & investigation_completed_date == lubridate::ymd("2025-10-24"))) %>% 
  #
  dplyr::filter(!event_classification %in% c("Not notifiable", "Rejected")) %>%
  #
  dplyr::arrange(phess_id, date_signed_dh) %>%
  #
  dplyr::distinct(phess_id, .keep_all = TRUE)
```


```{r}
# Cases of specified urgent conditions
nephu_urgent <- completed_nephu %>% 
  dplyr::filter(condition %in% incident_urgent) %>% 
  #
  dplyr::group_by(short_name) %>% 
  dplyr::summarise(n = n()) %>% 
  dplyr::ungroup()
```


```{r}
# Locally acquired specified urgent conditions
nephu_local <- completed_nephu %>% 
  dplyr::filter(condition %in% incident_local) %>% 
  dplyr::filter(is.na(travel_overseas)) %>% 
  #
  dplyr::group_by(short_name) %>% 
  dplyr::summarise(n = n()) %>% 
  dplyr::ungroup()
```


```{r}
# Cases of specified high consequence conditions
nephu_rare <- completed_nephu %>% 
  dplyr::filter(condition %in% incident_rare) %>% 
  #
  dplyr::group_by(short_name) %>% 
  dplyr::summarise(n = n()) %>% 
  dplyr::ungroup()
```


```{r}
# Overseas acquired specified enteric cases who work in high-risk occupation or attend childcare
nephu_highrisk <- completed_nephu %>% 
  dplyr::filter(condition %in% incident_highrisk) %>% 
  dplyr::filter(travel_overseas == "Yes") %>%
  dplyr::filter(work_status %in% c("Employed", "Child in child/day care"))

################################################################################
# Uncomment this section as required
################################################################################
# Create and export the linelist of cases that need manual checking
# nephu_highrisk <- nephu_highrisk %>%
#   dplyr::arrange(short_name,
#                  event_date) %>%
#   #
#   dplyr::mutate(event_date = format(event_date, "%d/%m/%Y")) %>%
#   #
#   dplyr::select(`PHESS ID` = phess_id,
#                 `Event date` = event_date,
#                 `Condition` = short_name,
#                 `Final event classification` = event_classification,
#                 `Work status` = work_status,
#                 `Occupation` = occupation) %>%
#   #
#   dplyr::mutate(`High risk` = "")
# 
# writexl::write_xlsx(nephu_highrisk,
#                     paste0(here::here(), "/Data", "/ManualReview_", "HighRisk_", format(quarter_end, format = "%Y%m%d"), ".xlsx"))
################################################################################
# Read in results of manual review
nephu_highrisk <- readxl::read_xlsx(paste0(here::here(), "/Data", "/ManualReview_", "HighRisk_", format(quarter_end, format = "%Y%m%d"), ".xlsx"),
                                   sheet     = 1,
                                   guess_max = min(100000, Inf)) %>%
  #
  janitor::clean_names()

nephu_highrisk <- nephu_highrisk %>% 
  dplyr::filter(high_risk == "Yes") %>% 
  #
  dplyr::rename(short_name = condition) %>% 
  #
  dplyr::group_by(short_name) %>% 
  dplyr::summarise(n = n()) %>% 
  dplyr::ungroup()
```


```{r}
# Invasive GAS where PEP provision was required
nephu_pep <- completed_nephu %>% 
  dplyr::filter(condition == "Invasive Group A Streptococcus")

################################################################################
# Uncomment this section as required
################################################################################
# Create and export the linelist of cases that need manual checking
# nephu_pep <- nephu_pep %>%
#   dplyr::arrange(short_name,
#                  event_date) %>%
#   #
#   dplyr::mutate(event_date = format(event_date, "%d/%m/%Y")) %>%
#   #
#   dplyr::select(`PHESS ID` = phess_id,
#                 `Event date` = event_date,
#                 `Condition` = short_name,
#                 `Final event classification` = event_classification) %>%
#   #
#   dplyr::mutate(`PEP provided` = "")
# 
# writexl::write_xlsx(nephu_pep,
#                     paste0(here::here(), "/Data", "/ManualReview_", "PEP_", format(quarter_end, format = "%Y%m%d"), ".xlsx"))
################################################################################
# Read in results of manual review
nephu_pep <- readxl::read_xlsx(paste0(here::here(), "/Data", "/ManualReview_", "PEP_", format(quarter_end, format = "%Y%m%d"), ".xlsx"),
                                   sheet     = 1,
                                   guess_max = min(100000, Inf)) %>%
  #
  janitor::clean_names()

nephu_pep <- nephu_pep %>% 
  dplyr::filter(pep_provided == "Yes") %>% 
  #
  dplyr::rename(short_name = condition) %>% 
  #
  dplyr::group_by(short_name) %>% 
  dplyr::summarise(n = n()) %>% 
  dplyr::ungroup()
```


```{r}
#
nephu_incident_cases <- nephu_urgent %>% 
  dplyr::bind_rows(nephu_local) %>% 
  dplyr::bind_rows(nephu_rare) %>% 
  dplyr::bind_rows(nephu_highrisk) %>% 
  dplyr::bind_rows(nephu_pep) %>% 
  #
  janitor::adorn_totals()

cases_total <- nephu_incident_cases %>% 
  dplyr::filter(short_name == "Total") %>% 
  pull(n)
```

:::{.infobox}
There were `r cases_total + outbreaks_total` Model 1 incidents (`r outbreaks_total` outbreaks and `r cases_total` cases) closed/completed by NEPHU between `r format(quarter_start, format = "%d/%m/%Y")` and `r format(quarter_end, format = "%d/%m/%Y")`. 
:::

:::{style="height: 1em;"}
:::

**Outbreaks closed between `r format(quarter_start, format = "%d/%m/%Y")` and `r format(quarter_end, format = "%d/%m/%Y")`, NEPHU, by causative organism**

```{r}
#
nephu_incident_outbreaks %>% 
  knitr::kable(table.attr = "style = \"color: black;\"",
               align      = "lr",
               col.names  = c("Condition",
                              "Closed outbreaks (n)")) %>%
  #
  kableExtra::kable_styling(full_width = FALSE,
                            position   = "center",
                            html_font  = "Arial",
                            font_size  = 12) %>%
  #
  kableExtra::row_spec(row  = 0,
                       bold = TRUE) %>%
  #
  kableExtra::row_spec(nrow(nephu_incident_outbreaks),
                       bold      = TRUE,
                       extra_css = "border-top: 2px solid lightgray; border-bottom: 2px solid lightgray;")
```

:::{style="height: 1em;"}
:::

**Model 1 incident cases completed between `r format(quarter_start, format = "%d/%m/%Y")` and `r format(quarter_end, format = "%d/%m/%Y")`, NEPHU, by condition**

```{r}
#
nephu_incident_cases %>% 
  knitr::kable(table.attr = "style = \"color: black;\"",
               align      = "lr",
               col.names  = c("Condition",
                              "Completed cases (n)")) %>%
  #
  kableExtra::kable_styling(full_width = FALSE,
                            position   = "center",
                            html_font  = "Arial",
                            font_size  = 12) %>%
  #
  kableExtra::row_spec(row  = 0,
                       bold = TRUE) %>%
  #
  kableExtra::row_spec(nrow(nephu_incident_cases),
                       bold      = TRUE,
                       extra_css = "border-top: 2px solid lightgray; border-bottom: 2px solid lightgray;")
```

<br/>

<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>
