---
title: 'DH Quarterly Reporting - Indigenous Status Completion'
author_details: "Alana Little, NEPHU (alana.little@austin.org.au)"
output: 
  html_document: 
    code_folding: none
    toc: true
    toc_depth: 3
    toc_float: true
knit: (function(input, ...) {
  rmarkdown::render(input, output_file = paste0("2026 Q4", " DH Quarterly Reporting", " Indigenous Status"), output_dir = "../Reports") })
---

```{css, echo = FALSE}
/* */ 
.main-container {
    max-width: 1000px;
}

h1.title {
  font-weight: bold;
  font-size: 20px;
  color: #191d43;
}

h1 {
  font-weight: bold;
  font-size: 20px;
  color: #5bc788;
}

h2 {
  font-weight: bold;
  font-size: 18px;
  color: #5bc788;
}

h3 {
  font-weight: bold;
  font-size: 16px;
  color: #5bc788;
}

body {
  font-size: 14px;
}

.infobox {
  padding-top: 10px;
  padding-left: 10px;
  padding-right: 10px;
  background: white;
  color: black;
  border: 2px solid #5BC788;
  border-radius: 10px;
}
```


```{r, echo = FALSE, message = FALSE}
#
knitr::opts_chunk$set(echo    = FALSE, 
                      warning = FALSE, 
                      message = FALSE)

options(knitr.kable.NA = '--')

source(paste0(here::here(), "/Code", "/00_setup.R"))
```


```{r}
#
source(paste0(here::here(), "/Code", "/00_data_extract.R"))
```

::: {style="height: 1em;"}
:::

::: {.infobox}
**Indicator SQ2.3**

**Proportion of notifiable condition events allocated to LPHUs that have reporting for Aboriginal and/or Torres Strait Islander status completed**

Numerator: Number of case and contact events marked as completed by NEPHU during the reporting period with Aboriginal and/or Torres Strait Islander status recorded

Denominator: Number of case and contact events marked as completed by NEPHU during the reporting period
:::

## All notifications completed during the reporting period

Data were extracted from PHESS via PHAR on `r format(Sys.Date(), format = "%d/%m/%Y")` for all notifiable conditions completed by NEPHU between `r format(quarter_start, format = "%d/%m/%Y")` and `r format(quarter_end, format = "%d/%m/%Y")`. 

* Both initial notifications and reinvestigations signed out for follow-up were included.

* Cases and contact/exposed persons were included.

* Confirmed, Probable, Suspected, and At Risk notifications were included.

* Rejected and Not Notifiable notifications were excluded.

* Conditions not managed by LPHUs (anaphylaxis, elevated blood lead, human biosecurity reports, and tuberculosis) were excluded.

Indigenous status was classified as recorded when the Indigenous status field in PHESS was any other option than "Missing/Not Stated". The "Missing/Not Stated" option includes situations where Indigenous status has been left blank on the ESF and/or the Indigenous status question was not asked during case interview (Missing) and situations where Indigenous status has been filled out on the ESF and/or asked during the case interview but the respondent has refused to answer the question, was lost to follow-up, or was unsure of their status (Not Stated). There is currently no way to separate out these options in PHESS.

::: {style="height: 1em;"}
:::

```{r}
# Select notifications signed out to NEPHU and with follow-up completed during reporting period
completed_nephu <- cases_nephu %>%
  dplyr::filter(!is.na(date_signed_dh)) %>% 
  dplyr::filter(investigation_status %in% c("Completed", "Reviewed") | reinvestigation_status %in% c("Completed", "Reviewed")) %>% 
  #
  dplyr::mutate(completed_quarter = dplyr::case_when(
    investigation_completed_date >= quarter_start & investigation_completed_date <= quarter_end ~ "Yes",
    reinvestigation_status_date >= quarter_start & reinvestigation_status_date <= quarter_end   ~ "Yes",
    TRUE ~ "No")) %>% 
  #
  dplyr::filter(completed_quarter == "Yes") %>%
  #
  dplyr::filter(!event_classification %in% c("Not notifiable", "Rejected")) %>%
  #
  dplyr::arrange(phess_id, date_signed_dh) %>%
  #
  dplyr::distinct(phess_id, .keep_all = TRUE)
```


```{r}
#
indigenous_completed <- completed_nephu %>%
  dplyr::group_by(reporting_group, short_name) %>% 
  dplyr::summarise(completed_n = n()) %>% 
  dplyr::ungroup() %>% 
  #
  dplyr::arrange(reporting_group, short_name)

indigenous_recorded <- completed_nephu %>%
  dplyr::filter(indigenous_status != "Missing/Not Stated") %>% 
  #
  dplyr::group_by(reporting_group, short_name) %>% 
  dplyr::summarise(recorded_n = n()) %>% 
  dplyr::ungroup() %>% 
  #
  dplyr::arrange(reporting_group, short_name)

indigenous_completed <- indigenous_completed %>% 
  dplyr::left_join(indigenous_recorded, by = c("reporting_group", "short_name")) %>%
  #
  replace_na(list(recorded_n = 0)) %>% 
  #
  janitor::adorn_totals() %>% 
  #
  dplyr::mutate(recorded_percent = round(recorded_n / completed_n * 100, digits = 1)) %>% 
  #
  dplyr::select(reporting_group,
                short_name,
                recorded_n,
                completed_n,
                recorded_percent)

indigenous_total <- indigenous_completed %>% 
  dplyr::filter(reporting_group == "Total")

# Calculate number of notifications with missing/not stated status where collection was attempted
indigenous_missing <- completed_nephu %>%
  dplyr::filter(indigenous_status == "Missing/Not Stated") %>% 
  nrow()

indigenous_attempted <- completed_nephu %>%
  dplyr::filter(indigenous_status == "Missing/Not Stated") %>%
  dplyr::filter(atsi_status_collection_attempted == "Collection attempted from physician or case") %>% 
  nrow()
```


```{r}
# Recalculate with gonorrhoea notifications excluded
indigenous_completed_exc <- completed_nephu %>%
  dplyr::filter(short_name != "Gonorrhoea") %>%
  #
  dplyr::group_by(reporting_group, short_name) %>% 
  dplyr::summarise(completed_n = n()) %>% 
  dplyr::ungroup() %>% 
  #
  dplyr::arrange(reporting_group, short_name)

indigenous_recorded_exc <- completed_nephu %>%
  dplyr::filter(short_name != "Gonorrhoea") %>% 
  dplyr::filter(indigenous_status != "Missing/Not Stated") %>% 
  #
  dplyr::group_by(reporting_group, short_name) %>% 
  dplyr::summarise(recorded_n = n()) %>% 
  dplyr::ungroup() %>% 
  #
  dplyr::arrange(reporting_group, short_name)

indigenous_completed_exc <- indigenous_completed_exc %>% 
  dplyr::left_join(indigenous_recorded_exc, by = c("reporting_group", "short_name")) %>%
  #
  replace_na(list(recorded_n = 0)) %>% 
  #
  janitor::adorn_totals() %>% 
  #
  dplyr::mutate(recorded_percent = round(recorded_n / completed_n * 100, digits = 1)) %>% 
  #
  dplyr::select(reporting_group,
                short_name,
                recorded_n,
                completed_n,
                recorded_percent)

indigenous_total_exc <- indigenous_completed_exc %>% 
  dplyr::filter(reporting_group == "Total")

# Calculate number of notifications with missing/not stated status where collection was attempted
indigenous_missing_exc <- completed_nephu %>%
  dplyr::filter(short_name != "Gonorrhoea") %>%
  dplyr::filter(indigenous_status == "Missing/Not Stated") %>% 
  nrow()

indigenous_attempted_exc <- completed_nephu %>%
  dplyr::filter(short_name != "Gonorrhoea") %>%
  dplyr::filter(indigenous_status == "Missing/Not Stated") %>%
  dplyr::filter(atsi_status_collection_attempted == "Collection attempted from physician or case") %>% 
  nrow()
```

::: {.infobox}
* `r round(indigenous_total$recorded_percent, digits = 1)`% (`r format(indigenous_total$recorded_n, big.mark = ",")`/`r format(indigenous_total$completed_n, big.mark = ",")`) of notifications completed by NEPHU between `r format(quarter_start, format = "%d/%m/%Y")` and `r format(quarter_end, format = "%d/%m/%Y")` had Indigenous status recorded (i.e. not recorded as "Missing/Not Stated") at the time of reporting.
  * For notifications with "Missing/Not Stated" Indigenous status, collection of Indigenous status was attempted from the physician or case for `r round(indigenous_attempted / indigenous_missing * 100, digits = 1)`% (`r format(indigenous_attempted, big.mark = ",")`/`r format(indigenous_missing, big.mark = ",")`) of these notifications.

<div style="height: 0.1em;"></div>

* If gonorrhoea notifications are excluded, `r round(indigenous_total_exc$recorded_percent, digits = 1)`% (`r format(indigenous_total_exc$recorded_n, big.mark = ",")`/`r format(indigenous_total_exc$completed_n, big.mark = ",")`) of notifications completed by NEPHU between `r format(quarter_start, format = "%d/%m/%Y")` and `r format(quarter_end, format = "%d/%m/%Y")` had Indigenous status recorded (i.e. not recorded as "Missing/Not Stated") at the time of reporting.
  * For notifications with "Missing/Not Stated" Indigenous status, collection of Indigenous status was attempted from the physician or case for `r round(indigenous_attempted_exc / indigenous_missing_exc * 100, digits = 1)`% (`r format(indigenous_attempted_exc, big.mark = ",")`/`r format(indigenous_missing_exc, big.mark = ",")`) of these notifications.

:::

::: {style="height: 1em;"}
:::

**Number and percentage of completed notifications between `r format(quarter_start, format = "%d/%m/%Y")` and `r format(quarter_end, format = "%d/%m/%Y")` with Indigenous status recorded, NEPHU**

```{r}
#
indigenous_completed %>% 
  dplyr::mutate(recorded_percent = sprintf("%.1f", recorded_percent)) %>%
  #
  knitr::kable(table.attr  = "style = \"color: black;\"",
               format.args = list(big.mark = ","),
               align       = "llrrr",
               col.names   = c("Reporting group",
                               "Condition",
                               "Indigenous status recorded (n)",
                               "Completed cases (n)",
                               "Completed cases with Indigenous status recorded (%)")) %>% 
  #
  kableExtra::kable_styling(full_width = FALSE,
                            position   = "center",
                            html_font  = "Arial",
                            font_size  = 12) %>%
  #
  kableExtra::column_spec(3:5,
                          width = "1.5in") %>% 
  #
  kableExtra::row_spec(row  = 0,
                       bold = TRUE) %>% 
  #
  kableExtra::row_spec(nrow(indigenous_completed),
                       bold      = TRUE,
                       extra_css = "border-top: 2px solid lightgray; border-bottom: 2px solid lightgray;") %>% 
  #
  kableExtra::scroll_box(height = "400px")
```

::: {style="height: 1em;"}
:::

**Indigenous status for completed notifications between `r format(quarter_start, format = "%d/%m/%Y")` and `r format(quarter_end, format = "%d/%m/%Y")` with Indigenous status recorded, NEPHU**

```{r}
#
status_nephu <- completed_nephu %>%
  dplyr::filter(indigenous_status != "Missing/Not Stated") %>%
  #
  dplyr::mutate(indigenous_status = factor(indigenous_status,
                                           levels = c("Aboriginal and Torres Strait Islander origin",
                                                      "Aboriginal but not Torres Strait Islander origin",
                                                      "Torres Strait Islander but not Aboriginal origin",
                                                      "Not Aboriginal or Torres Strait Islander",
                                                      "Declined to answer"))) %>% 
  #
  dplyr::group_by(indigenous_status) %>% 
  dplyr::summarise(n = n()) %>% 
  dplyr::ungroup() %>% 
  #
  janitor::adorn_totals()

status_nephu %>% 
  knitr::kable(table.attr  = "style = \"color: black;\"",
               format.args = list(big.mark = ","),
               align       = "lr",
               col.names   = c("Indigenous status (n)",
                               "Completed cases (n)")) %>% 
  #
  kableExtra::kable_styling(full_width = FALSE,
                            position   = "center",
                            html_font  = "Arial",
                            font_size  = 12) %>%
  #
  kableExtra::row_spec(row  = 0,
                       bold = TRUE) %>% 
  #
  kableExtra::row_spec(nrow(status_nephu),
                       bold      = TRUE,
                       extra_css = "border-top: 2px solid lightgray; border-bottom: 2px solid lightgray;")
```

### Completed routine notifications with Indigenous status missing

Data were extracted from PHESS via PHAR on `r format(Sys.Date(), format = "%d/%m/%Y")` for all routine notifiable conditions signed out from the Department of Health to NEPHU between `r format(quarter_start, format = "%d/%m/%Y")` and `r format(quarter_end, format = "%d/%m/%Y")`. 

* Both initial notifications and reinvestigations signed out for follow-up were included.

* Cases and contact/exposed persons were included.

* Confirmed, Probable, Suspected, and At Risk notifications were included.

* Rejected and Not Notifiable notifications were excluded.

Urgent notifiable conditions include the following: anthrax, botulism, *Candida auris*, cholera, diphtheria, haemolytic uraemic syndrome, *Haemophilus influenzae* type B, Hepatitis A, invasive Group A *Streptococcus*, invasive meningococcal disease, Japanese encephalitis, legionellosis, listeriosis, lyssavirus (Australian Bat Lyssavirus, rabies, and others), measles, Middle East Respiratory Syndrome, mpox, Murray Valley encephalitis, paratyphoid, plague, poliomyelitis, Severe Acute Respiratory Syndrome, smallpox, tularaemia, typhoid, viral haemorrhagic fevers, and yellow fever. Routine notifiable conditions include all other notifiable conditions. 

Indigenous status was classified as recorded when the Indigenous status field in PHESS was any other option than "Missing/Not Stated". The "Missing/Not Stated" option includes situations where Indigenous status has been left blank on the ESF and/or the Indigenous status question was not asked during case interview (Missing) and situations where Indigenous status has been filled out on the ESF and/or asked during the case interview but the respondent has refused to answer the question, was lost to follow-up, or was unsure of their status (Not Stated). There is currently no way to separate out these options in PHESS.

::: {style="height: 1em;"}
:::

```{r}
################################################################################ 
# Uncomment this code chunk as required
################################################################################
# Create and export the linelist of routine cases that need manual checking
# Exclude gonorrhoea notifications
# Exclude notifications where collection known to have attempted
# indigenous_missing <- completed_nephu %>%
#   dplyr::filter(investigation_status %in% c("Completed", "Reviewed")) %>%
#   dplyr::filter(indigenous_status == "Missing/Not Stated") %>%
#   dplyr::filter(!condition %in% conditions_urgent) %>%
#   dplyr::filter(short_name != "Gonorrhoea") %>%
#   #
#   dplyr::arrange(short_name, event_date) %>%
#   #
#   dplyr::mutate(event_date     = format(event_date, "%d/%m/%Y"),
#                 date_signed_dh = format(date_signed_dh, "%d/%m/%Y")) %>%
#   #
#   dplyr::select(`PHESS ID` = phess_id,
#                 `Event date` = event_date,
#                 `Condition` = short_name,
#                 `Final event classification` = event_classification,
#                 `Signed out by DH` = date_signed_dh,
#                 atsi_status_collection_attempted) %>%
#   #
#   dplyr::mutate(`Collection attempted` = dplyr::case_when(!is.na(atsi_status_collection_attempted) ~ "Yes",
#                                                           TRUE ~ "No record"),
#                 `Notes` = "") %>%
#   #
#   dplyr::select(-atsi_status_collection_attempted) %>%
#   #
#   dplyr::arrange(`Collection attempted`, `Condition`)
# 
# writexl::write_xlsx(indigenous_missing,
#                     paste0(here::here(), "/Data", "/ManualReview_", "IndigenousPendingRoutine_", format(quarter_end, format = "%Y%m%d"), ".xlsx"))
```

**Routine notifications signed out between `r format(quarter_start, format = "%d/%m/%Y")` and `r format(quarter_end, format = "%d/%m/%Y")` with Indigenous status "Missing/Not Stated", gonorrhoea notifications excluded, NEPHU**

```{r}
# Read in results of manual review
indigenous_missing <- readxl::read_xlsx(paste0(here::here(), "/Data", "/ManualReview_", "IndigenousPendingRoutine_",
                                               format(quarter_end, format = "%Y%m%d"), ".xlsx"),

                                        sheet     = 1,
                                        guess_max = min(100000, Inf)) %>%
  #
  janitor::clean_names()

table_routine <- indigenous_missing %>%
  knitr::kable(table.attr  = "style = \"color: black;\"",
               format.args = list(big.mark = ","),
               align       = "lcllcll",
               col.names   = c("PHESS ID",
                               "Notification date",
                               "Condition",
                               "Classification",
                               "Sign-out date",
                               "Indigenous status requested",
                               "Notes")) %>%
  #
  kableExtra::kable_styling(full_width = FALSE,
                            position   = "center",
                            html_font  = "Arial",
                            font_size  = 12) %>%
  #
  kableExtra::column_spec(c(2, 5),
                          width = "1.5in") %>%
  #
  kableExtra::row_spec(row  = 0,
                       bold = TRUE) %>%
  #
  kableExtra::row_spec(nrow(indigenous_missing),
                       extra_css = "border-bottom: 2px solid lightgray;") %>% 
  #
  kableExtra::scroll_box(height = "400px")
```

`r if(nrow(indigenous_missing) == 0) paste0("There were no routine notifications with *Missing/Not Stated* Indigenous status.")`

`r if(nrow(indigenous_missing) > 0) table_routine`

***

## Urgent notifications completed during the reporting period

Data were extracted from PHESS via PHAR on `r format(Sys.Date(), format = "%d/%m/%Y")` for all notifiable conditions completed by NEPHU between `r format(quarter_start, format = "%d/%m/%Y")` and `r format(quarter_end, format = "%d/%m/%Y")`.

* Both initial notifications and reinvestigations signed out for follow-up were included.

* Cases and contact/exposed persons were included.

* Confirmed, Probable, Suspected, and At Risk notifications were included.

* Rejected and Not Notifiable notifications were excluded.

* Conditions not managed by LPHUs (anaphylaxis, elevated blood lead, human biosecurity reports, and tuberculosis) were excluded.

Urgent notifiable conditions include the following: anthrax, botulism, *Candida auris*, cholera, diphtheria, haemolytic uraemic syndrome, *Haemophilus influenzae* type B, Hepatitis A, invasive Group A *Streptococcus*, invasive meningococcal disease, Japanese encephalitis, legionellosis, listeriosis, lyssavirus (Australian Bat Lyssavirus, rabies, and others), measles, Middle East Respiratory Syndrome, mpox, Murray Valley encephalitis, paratyphoid, plague, poliomyelitis, Severe Acute Respiratory Syndrome, smallpox, tularaemia, typhoid, viral haemorrhagic fevers, and yellow fever.

Indigenous status was classified as recorded when the Indigenous status field in PHESS was any other option than "Missing/Not Stated". The "Missing/Not Stated" option includes situations where Indigenous status has been left blank on the ESF and/or the Indigenous status question was not asked during case interview (Missing) and situations where Indigenous status has been filled out on the ESF and/or asked during the case interview but the respondent has refused to answer the question, was lost to follow-up, or was unsure of their status (Not Stated). There is currently no way to separate out these options in PHESS.

::: {style="height: 1em;"}
:::

```{r}
#
indigenous_completed <- completed_nephu %>%
  dplyr::filter(condition %in% conditions_urgent) %>% 
  #
  dplyr::group_by(reporting_group, short_name) %>% 
  dplyr::summarise(completed_n = n()) %>% 
  dplyr::ungroup() %>% 
  #
  dplyr::arrange(reporting_group, short_name)

indigenous_recorded <- completed_nephu %>%
  dplyr::filter(condition %in% conditions_urgent) %>%
  #
  dplyr::filter(indigenous_status != "Missing/Not Stated") %>% 
  #
  dplyr::group_by(reporting_group, short_name) %>% 
  dplyr::summarise(recorded_n = n()) %>% 
  dplyr::ungroup() %>% 
  #
  dplyr::arrange(reporting_group, short_name)

indigenous_completed <- indigenous_completed %>% 
  dplyr::left_join(indigenous_recorded, by = c("reporting_group", "short_name")) %>%
  #
  replace_na(list(recorded_n = 0)) %>% 
  #
  janitor::adorn_totals() %>% 
  #
  dplyr::mutate(recorded_percent = round(recorded_n / completed_n * 100, digits = 1)) %>% 
  #
  dplyr::select(reporting_group,
                short_name,
                recorded_n,
                completed_n,
                recorded_percent)

indigenous_total <- indigenous_completed %>% 
  dplyr::filter(reporting_group == "Total")
```

:::{.infobox}
`r round(indigenous_total$recorded_percent, digits = 1)`% (`r format(indigenous_total$recorded_n, big.mark = ",")`/`r format(indigenous_total$completed_n, big.mark = ",")`) of urgent notifications completed by NEPHU between `r format(quarter_start, format = "%d/%m/%Y")` and `r format(quarter_end, format = "%d/%m/%Y")` had Indigenous status recorded (i.e. not recorded as "Missing/Not Stated") at the time of reporting.
:::

::: {style="height: 1em;"}
:::

**Number and percentage of completed urgent notifications between `r format(quarter_start, format = "%d/%m/%Y")` and `r format(quarter_end, format = "%d/%m/%Y")` with Indigenous status recorded, NEPHU**

```{r}
#
indigenous_completed %>% 
  dplyr::mutate(recorded_percent = sprintf("%.1f", recorded_percent)) %>%
  #
  knitr::kable(table.attr  = "style = \"color: black;\"",
               format.args = list(big.mark = ","),
               align       = "llrrr",
               col.names   = c("Reporting group",
                               "Condition",
                               "Indigenous status recorded (n)",
                               "Completed cases (n)",
                               "Completed cases with Indigenous status recorded (%)")) %>% 
  #
  kableExtra::kable_styling(full_width = FALSE,
                            position   = "center",
                            html_font  = "Arial",
                            font_size  = 12) %>%
  #
  kableExtra::column_spec(3:5,
                          width = "1.5in") %>% 
  #
  kableExtra::row_spec(row  = 0,
                       bold = TRUE) %>% 
  #
  kableExtra::row_spec(nrow(indigenous_completed),
                       bold      = TRUE,
                       extra_css = "border-top: 2px solid lightgray; border-bottom: 2px solid lightgray;")
```

***

### Completed urgent notifications with Indigenous status missing

Data were extracted from PHESS via PHAR on `r format(Sys.Date(), format = "%d/%m/%Y")` for all urgent notifiable conditions signed out from the Department of Health to NEPHU between `r format(quarter_start, format = "%d/%m/%Y")` and `r format(quarter_end, format = "%d/%m/%Y")`. 

* Both initial notifications and reinvestigations signed out for follow-up were included.

* Cases and contact/exposed persons were included.

* Confirmed, Probable, Suspected, and At Risk notifications were included.

* Rejected and Not Notifiable notifications were excluded.

Urgent notifiable conditions include the following: anthrax, botulism, *Candida auris*, cholera, diphtheria, haemolytic uraemic syndrome, *Haemophilus influenzae* type B, Hepatitis A, invasive Group A *Streptococcus*, invasive meningococcal disease, Japanese encephalitis, legionellosis, listeriosis, lyssavirus (Australian Bat Lyssavirus, rabies, and others), measles, Middle East Respiratory Syndrome, mpox, Murray Valley encephalitis, paratyphoid, plague, poliomyelitis, Severe Acute Respiratory Syndrome, smallpox, tularaemia, typhoid, viral haemorrhagic fevers, and yellow fever.

Indigenous status was classified as recorded when the Indigenous status field in PHESS was any other option than "Missing/Not Stated". The "Missing/Not Stated" option includes situations where Indigenous status has been left blank on the ESF and/or the Indigenous status question was not asked during case interview (Missing) and situations where Indigenous status has been filled out on the ESF and/or asked during the case interview but the respondent has refused to answer the question, was lost to follow-up, or was unsure of their status (Not Stated). There is currently no way to separate out these options in PHESS.

::: {style="height: 1em;"}
:::

```{r}
################################################################################ 
# Uncomment this code chunk as required
################################################################################
# Create and export the linelist of urgent cases that need manual checking
# 
# indigenous_missing <- completed_nephu %>%
#   dplyr::filter(investigation_status %in% c("Completed", "Reviewed")) %>%
#   dplyr::filter(condition %in% conditions_urgent) %>%
#   dplyr::filter(indigenous_status == "Missing/Not Stated") %>%
#   #
#   dplyr::arrange(short_name, event_date) %>%
#   #
#   dplyr::mutate(event_date     = format(event_date, "%d/%m/%Y"),
#                 date_signed_dh = format(date_signed_dh, "%d/%m/%Y")) %>%
#   #
#   dplyr::select(`PHESS ID` = phess_id,
#                 `Event date` = event_date,
#                 `Condition` = short_name,
#                 `Final event classification` = event_classification,
#                 `Signed out by DH` = date_signed_dh,
#                 atsi_status_collection_attempted) %>%
#   #
#   dplyr::mutate(`Collection attempted` = dplyr::case_when(!is.na(atsi_status_collection_attempted) ~ "Yes",
#                                                           TRUE ~ "No record"),
#                 `Notes` = "") %>%
#   #
#   dplyr::select(-atsi_status_collection_attempted) %>%
#   #
#   dplyr::arrange(`Collection attempted`, `Condition`)
# 
# writexl::write_xlsx(indigenous_missing,
#                     paste0(here::here(), "/Data", "/ManualReview_", "IndigenousPendingUrgent_", format(quarter_end, format = "%Y%m%d"), ".xlsx"))
```

**Urgent notifications signed out between `r format(quarter_start, format = "%d/%m/%Y")` and `r format(quarter_end, format = "%d/%m/%Y")` with Indigenous status missing, NEPHU**

```{r}
# Read in results of manual review
indigenous_missing <- readxl::read_xlsx(paste0(here::here(), "/Data", "/ManualReview_", "IndigenousPendingUrgent_", 
                                               format(quarter_end, format = "%Y%m%d"), ".xlsx"),

                                        sheet     = 1,
                                        guess_max = min(100000, Inf)) %>%
  #
  janitor::clean_names()

table_urgent <- indigenous_missing %>%
  knitr::kable(table.attr  = "style = \"color: black;\"",
               format.args = list(big.mark = ","),
               align       = "lcllcll",
               col.names   = c("PHESS ID",
                               "Notification date",
                               "Condition",
                               "Classification",
                               "Sign-out date",
                               "Indigenous status requested",
                               "Notes")) %>%
  #
  kableExtra::kable_styling(full_width = FALSE,
                            position   = "center",
                            html_font  = "Arial",
                            font_size  = 12) %>%
  #
  kableExtra::column_spec(c(2, 5),
                          width = "1.5in") %>%
  #
  kableExtra::row_spec(row  = 0,
                       bold = TRUE) %>%
  #
  kableExtra::row_spec(nrow(indigenous_missing),
                       extra_css = "border-bottom: 2px solid lightgray;")
```

`r if(nrow(indigenous_missing) == 0) paste0("There were no urgent notifications with *Missing/Not Stated* Indigenous status.")`

`r if(nrow(indigenous_missing) > 0) table_urgent`

<br/>

<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>

